Quantifying the global film festival circuit:<br>interactive online supplementary

### 2023-04-24 cinandofestivals/index.qmd
update

---
title: "Quantifying the global film festival circuit:<br>interactive online supplementary"
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
format: 
  html:
    background-color: white
    fig-width: 9
    fig-height: 6
    out-width: "100%"
    embed-resources: true
    toc: true
    toc-location: left
    toc-depth: 6
    search: false
    grid:
      sidebar-width: 200px
      body-width: 1300px
      margin-width: 0px
editor: source
---

@@

  g={ggplot(vecs , 
        aes(exdiv, indiv, shape=ab, color=colorgenre, size=ab, text=tool))+
      geom_vline(xintercept = median(vecs$exdiv, na.rm=T) # mean(c(min(vecs$exdiv,na.rm=T), max(vecs$exdiv,na.rm=T)))
                 , color="gray25")+
      geom_hline(yintercept = median(vecs$indiv, na.rm=T)
                #   mean(c(min(vecs$indiv,na.rm=T), max(vecs$indiv,na.rm=T)))
                 , color="gray25")+
      geom_point(#data=vecs %>% filter(!(libelleFestival_NEW_VZ%in%ex)), 
                 alpha=0.7) +
      #geom_point(data=vecs %>% filter((libelleFestival_NEW_VZ%in%ex)), alpha=1)+
    #geom_line(aes(YearEvent, indiv), data=festvecs %>% group_by(YearEvent) %>% summarise(indiv=mean(indiv,na.rm=T)), inherit.aes = F)+
    # geom_path(aes(group=libelleFestival_NEW_VZ), 
    #           vecs %>% filter(libelleFestival_NEW_VZ%in%ex) ,
    #           color="black", 
    #           size=0.2)+
    #scale_color_manual(values=abcols)+
    scale_color_manual(values=genrecols, name=colorlab)+
    scale_shape_manual(values=abshapes, name="Festival")+
    scale_size_manual(values=c(2, 1.2), guide = "none")+
    labs(x=xlab, y=ylab)+
    theme_bw()+
    theme(#legend.position = 'left', 
      #panel.border = element_blank(),
      panel.grid.minor.x = element_blank(),
      plot.background = element_rect(color="white", fill="white")
    )} 
  if(convert){
    ggplotly(g,tooltip="text")
  } else {
    g
  }
}

@@

Film festivals as a network of events, connected if they share overlap in programming, below as a unipartite spring-embedded network diagram.

@@

fig_thematic = ggplot(mapping= aes(V1, V2))+
  #geom_pie_glyph(radius=0.16, slices=attr(pies2, "mains"))+
  geom_point(aes(text=tool, color=colorgenre, shape=ab), 
             data=ugenre %>% filter(type=="festival"), 
              alpha=0.9)+
   # geom_path(data=pies2 %>% ungroup %>%  filter(libelleFestival_NEW_VZ==exchange[1]) %>% select(V1, V2) %>% xspline(shape=-0.2, lwd=2, draw=F) %>% data.frame() %>% rename(V1=x,V2=y) , linewidth=0.5, arrow=arrow(angle=25, length=unit(0.06, "inch"), type="closed"), color="gray10", alpha=0.5)+
  #geom_point(aes(color=colorgenre), data=ugenre %>% filter(type=="film"), size=0.2, fill=NA,show.legend = FALSE)+
  geom_text(aes(label=event,color=colorgenre, size=sizegen %>% log),
                  data=ugenre %>%
                    filter(type %in% c("genre", "film")) %>%
                    group_by(type) %>%
                    filter(type=="genre" | (type=="film" & ( (1:n()) %in% c(15,7, 8, 10, 23, 5)) ) )
                    #mutate(event=case_when(type=="film"~as.character(1:n()), T~type))
                    ,
            lineheight=0.55,
            alpha=0.9, hjust=1,
            bg.color=alpha("white", 0.7),
            show.legend = FALSE, max.overlaps=1000,
            box.padding = 0.2, point.padding = 10, min.segment.length = 999,
            force_pull=0.1,force=2,  max.time = 2, guide="none")+
  #scale_size_continuous(c(2.8,3.6), guide="none")+
  #scale_radius_manual(values=c(0.2, 0.14), guide="none")+
  scale_shape_manual(values=abshapes, name="Festival\ntype")+

@@

  #scale_fill_manual(values=sixgcols, name="", breaks=attr(pies2, "mains") )+
  scale_color_manual(values=sixgcols, breaks=ugenre$colorgenre %>% levels )+
  scale_x_continuous(expand=c(0.01,0))+
  scale_y_continuous(expand=c(0.01,0))+
  theme_void()+
  theme(plot.tag=element_text(face = "bold",hjust=0,vjust=1, margin=margin(0,-9,-10,0)))+
  theme(legend.position = c(0.75,0.2),
        plot.background = element_rect( fill="white")
  )
gg(fig_thematic)
```

@@

fig_world = ggplot()+
  #geom_text(aes(V1, V2, color=colorgenre,label=libelleFestival_NEW_VZ), data=ulang %>% sample_n(30), size=3, show.legend = F, inherit.aes = F, alpha=0.9)+
  geom_polygon(mapping= aes(long, lat, group = group), data=mp, inherit.aes = F, color="gray80", fill=NA, size=0.1)+
  #geom_pie_glyph(aes(long, lat), radius=0.13, data=piesg, slices=attr(piesg, "mains"))+
  geom_point(aes(long, lat, color=colorgenre, shape=ab, text=tool), data=festcountryvecs 
             , size=1)+
  #scale_size(range=c(0.3,0.1), guide="none")+
  #scale_radius_manual(values=c(0.16, 0.12), guide="none")+
  scale_shape_manual(values=abshapes, name="Festival\ntype")+
  scale_color_manual(values=sixcols, 
    name="Main", breaks=levels(festcountryvecs$colorgenre)
                     )+ # add breaks if multiple geoms
  coord_cartesian(xlim=range(festcountryvecs$long)*1.01, ylim=range(festcountryvecs$lat)*1.03,expand=F)+
  theme_void()+
  theme(plot.tag=element_text(face = "bold",hjust=0,vjust=1, margin=margin(0,-9,-10,0)))+
  theme(legend.position = c(0.08,0.27),
        legend.background = element_rect(color="transparent", fill="transparent"),
    plot.background = element_rect( fill="white"),
    axis.text = element_text(size=3.8)
  )+
  NULL
gg(fig_world)
```

@@

  geom_point(aes( text=tool, color=colorgenre, shape=ab), data=ulang  , size=0.6)+
  #scale_size(range=c(0.3,0.1), guide="none")+
  #scale_radius_manual(values=c(0.16, 0.12), guide="none")+
  scale_shape_manual(values=abshapes, name="Festival\ntype")+
  scale_color_manual(values=langcols, 
    name="Main", breaks=levels(ulang$colorgenre)
                     )+ # add breaks if multiple geoms
  theme_void()+
  #labs(tag="C")+
  theme(plot.tag=element_text(face = "bold",hjust=0,vjust=1, margin=margin(0,-9,-10,0)))+
  scale_x_continuous(expand=c(0.005,0))+
  theme(legend.position = c(0.07,0.28),
        legend.background = element_rect(color="transparent", fill="transparent"),
    plot.background = element_rect( fill="white")
  )+
  NULL
gg(fig_langmap)

@@

>>>>

---
title: "Quantifying the global film festival circuit:<br>interactive online supplementary"
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
format: 
  html:
    background-color: white
    fig-width: 9
    fig-height: 6
    out-width: "100%"
    embed-resources: true
    toc: true
    toc-location: left
    toc-title: "Quantifying the global film festival circuit"
    toc-depth: 6
    toc-expand: 10
    search: false
    grid:
      sidebar-width: 200px
      body-width: 1300px
      margin-width: 0px
editor: source
---

@@

  g={ggplot(vecs , 
        aes(exdiv, indiv, shape=ab, color=colorgenre, size=ab, text=tool))+
      geom_vline(xintercept = median(vecs$exdiv, na.rm=T) # mean(c(min(vecs$exdiv,na.rm=T), max(vecs$exdiv,na.rm=T)))
                 , color="gray25")+
      geom_hline(yintercept = median(vecs$indiv, na.rm=T)
                #   mean(c(min(vecs$indiv,na.rm=T), max(vecs$indiv,na.rm=T)))
                 , color="gray25")+
      geom_point(#data=vecs %>% filter(!(libelleFestival_NEW_VZ%in%ex)), 
                 alpha=0.7) +
      #geom_point(data=vecs %>% filter((libelleFestival_NEW_VZ%in%ex)), alpha=1)+
    #geom_line(aes(YearEvent, indiv), data=festvecs %>% group_by(YearEvent) %>% summarise(indiv=mean(indiv,na.rm=T)), inherit.aes = F)+
    # geom_path(aes(group=libelleFestival_NEW_VZ), 
    #           vecs %>% filter(libelleFestival_NEW_VZ%in%ex) ,
    #           color="black", 
    #           size=0.2)+
    #scale_color_manual(values=abcols)+
    scale_color_manual(values=genrecols, name="")+
    scale_shape_manual(values=abshapes, name="")+
    scale_size_manual(values=c(2, 1.2), guide = "none", name="")+
    labs(x=xlab, y=ylab)+
    theme_bw()+
    theme(#legend.position = 'left', 
      #panel.border = element_blank(),
      panel.grid.minor.x = element_blank(),
      plot.background = element_rect(color="white", fill="white")
    )} 
  if(convert){
    ggplotly(g,tooltip="text")
  } else {
    g
  }
}

@@

Film festivals as a network of events, connected if they share overlap in programming, below as a unipartite spring-embedded network diagram. A-list festivals are blue, B are yellow.

@@

fig_thematic = ggplot(mapping= aes(V1, V2))+
  #geom_pie_glyph(radius=0.16, slices=attr(pies2, "mains"))+
  geom_point(aes(text=tool, color=colorgenre, shape=ab), 
             data=ugenre %>% filter(type=="festival"), 
              alpha=0.9)+
   # geom_path(data=pies2 %>% ungroup %>%  filter(libelleFestival_NEW_VZ==exchange[1]) %>% select(V1, V2) %>% xspline(shape=-0.2, lwd=2, draw=F) %>% data.frame() %>% rename(V1=x,V2=y) , linewidth=0.5, arrow=arrow(angle=25, length=unit(0.06, "inch"), type="closed"), color="gray10", alpha=0.5)+
  #geom_point(aes(color=colorgenre), data=ugenre %>% filter(type=="film"), size=0.2, fill=NA,show.legend = FALSE)+
  geom_text(aes(label=event,color=colorgenre, size=sizegen %>% log),
                  data=ugenre %>%
                    filter(type %in% c("genre", "film")) %>%
                    group_by(type) %>%
                    filter(type=="genre" | (type=="film" & ( (1:n()) %in% c(15,7, 8, 10, 23, 5)) ) )
                    #mutate(event=case_when(type=="film"~as.character(1:n()), T~type))
                    ,
            lineheight=0.55,
            alpha=0.9, hjust=1,
            bg.color=alpha("white", 0.7),
            show.legend = FALSE, max.overlaps=1000,
            box.padding = 0.2, point.padding = 10, min.segment.length = 999,
            force_pull=0.1,force=2,  max.time = 2, guide="none")+
  #scale_size_continuous(c(2.8,3.6), guide="none")+
  #scale_radius_manual(values=c(0.2, 0.14), guide="none")+
  scale_shape_manual(values=abshapes, name="Festival\ntype\nand\nmain\ngenre")+

@@

  #scale_fill_manual(values=sixgcols, name="", breaks=attr(pies2, "mains") )+
  scale_color_manual(values=sixgcols, breaks=ugenre$colorgenre %>% levels, name="" )+
  scale_x_continuous(expand=c(0.01,0))+
  scale_y_continuous(expand=c(0.01,0))+
  theme_void()+
  theme(plot.tag=element_text(face = "bold",hjust=0,vjust=1, margin=margin(0,-9,-10,0)))+
  theme(legend.position = c(0.75,0.2),
        plot.background = element_rect( fill="white")
  )
gg(fig_thematic)
```

@@

fig_world = ggplot()+
  #geom_text(aes(V1, V2, color=colorgenre,label=libelleFestival_NEW_VZ), data=ulang %>% sample_n(30), size=3, show.legend = F, inherit.aes = F, alpha=0.9)+
  geom_polygon(mapping= aes(long, lat, group = group), data=mp, inherit.aes = F, color="gray80", fill=NA, size=0.1)+
  #geom_pie_glyph(aes(long, lat), radius=0.13, data=piesg, slices=attr(piesg, "mains"))+
  geom_point(aes(long, lat, color=colorgenre, shape=ab, text=tool), data=festcountryvecs 
             , size=1)+
  #scale_size(range=c(0.3,0.1), guide="none")+
  #scale_radius_manual(values=c(0.16, 0.12), guide="none")+
  scale_shape_manual(values=abshapes, name="Festival\ntype\nand\nmain\ncountry")+
  scale_color_manual(values=sixcols, 
    name="Main", breaks=levels(festcountryvecs$colorgenre)
                     )+ # add breaks if multiple geoms
  coord_cartesian(xlim=range(festcountryvecs$long)*1.01, ylim=range(festcountryvecs$lat)*1.03,expand=F)+
  theme_void()+
  theme(plot.tag=element_text(face = "bold",hjust=0,vjust=1, margin=margin(0,-9,-10,0)))+
  theme(legend.position = c(0.08,0.27),
        legend.background = element_rect(color="transparent", fill="transparent"),
    plot.background = element_rect( fill="white"),
    axis.text = element_text(size=3.8)
  )+
  NULL
gg(fig_world)
```

@@

  geom_point(aes( text=tool, color=colorgenre, shape=ab), data=ulang  , size=0.6)+
  #scale_size(range=c(0.3,0.1), guide="none")+
  #scale_radius_manual(values=c(0.16, 0.12), guide="none")+
  scale_shape_manual(values=abshapes, name="Festival\ntype\nand\nmain\nlang.")+
  scale_color_manual(values=langcols, 
    name="Main", breaks=levels(ulang$colorgenre)
                     )+ # add breaks if multiple geoms
  theme_void()+
  #labs(tag="C")+
  theme(plot.tag=element_text(face = "bold",hjust=0,vjust=1, margin=margin(0,-9,-10,0)))+
  scale_x_continuous(expand=c(0.005,0))+
  theme(legend.position = c(0.07,0.28),
        legend.background = element_rect(color="transparent", fill="transparent"),
    plot.background = element_rect( fill="white")
  )+
  NULL
gg(fig_langmap)

@@

```{r, eval=T}
